Dependent Object Types

### 2012-08-08 article.tex
align
playing with the -1

Declaration subsumption is extended to a binary relation between
sequences of declarations as follows: $\seq{D} <: \seq{D'}$ iff
$\forall D'_i \exists D_j. D_j \sub D'_i$.

@@

\subsubsection{Set of Terms}
$\rele k \Gamma s T$ defines the set of terms that appear to have type
$T$ when taking at most $k$ steps. $s$ must agree with a {\it prefix}
of $\Gamma$, so $\Gamma$ can additionally contain variables not in
$s$. This is needed for checking methods in $\mathcal{V}$ above, and
for relating open terms. If $k > 0$, $\mathcal{E}$ extends $\Gamma$
and $s$ so that they agree. It then states that if it can reduce $t$
in the extended store to an irreducible term in $j < k$ steps, then
this term must be in a corresponding $\mathcal{V}$ set.
\begin{align*}
&\rele k \Gamma s T = \{ t \ |\\
&\gap \Gamma \ts T \wfe \andl\\
&\gap k = 0 \orl (\forall j \leq k,\\
&\gap\gap \forall (\Gamma'; s') \in \rels k \Gamma s ,\\
&\gap\gap \reductionl t {s'} {t'} {s''} j \andl\\
&\gap\gap \irred {t'} {s''} \impliesl\\
&\gap\gap \forall \Gamma'' \in \relg k {s''} {\Gamma'} ,\\
&\gap\gap {t'} \in \relv {k-j-1} {\Gamma''} {s''} T)\\
&\}
\end{align*}

@@

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma \emptyset T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma''}
{s'} T$ by supposing $k > 0$, $(\Gamma'; s) \in \rels k \Gamma \emptyset$, and, for some
$j \leq k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl {\Gamma''} \in \relg \Gamma k {s'} {\Gamma'}$.

>>>>

Declaration subsumption is extended to a binary relation between
sequences of declarations: $\seq{D} <: \seq{D'}$ iff $\forall D'_i,
\exists D_j. {D_j \sub D'_i}$.

@@

\subsubsection{Set of Terms}
$\rele k \Gamma s T$ defines the set of terms that appear to have type
$T$ when taking at most $k$ steps. $s$ must agree with a {\it prefix}
of $\Gamma$, so $\Gamma$ can additionally contain variables not in
$s$. This is needed for checking methods in $\mathcal{V}$ above, and
for relating open terms. If $k > 0$, $\mathcal{E}$ extends $\Gamma$
and $s$ so that they agree. It then states that if it can reduce $t$
in the extended store to an irreducible term in $j < k$ steps, then
this term must be in a corresponding $\mathcal{V}$ set.
\begin{align*}
&\rele k \Gamma s T = \{ t \ |\\
&\gap \Gamma \ts T \wfe \andl\\
&\gap k = 0 \orl (\forall j < k,\\
&\gap\gap \forall (\Gamma'; s') \in \rels k \Gamma s ,\\
&\gap\gap \reductionl t {s'} {t'} {s''} j \andl\\
&\gap\gap \irred {t'} {s''} \impliesl\\
&\gap\gap \forall \Gamma'' \in \relg k {s''} {\Gamma'} ,\\
&\gap\gap {t'} \in \relv {k-j-1} {\Gamma''} {s''} T)\\
&\}
\end{align*}

@@

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma \emptyset T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma''}
{s'} T$ by supposing $k > 0$, $(\Gamma'; s) \in \rels k \Gamma \emptyset$, and, for some
$j < k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl {\Gamma''} \in \relg \Gamma k {s'} {\Gamma'}$.
